(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} via D-D Neutron Generator\\ OR \\(n,p) Cross-Section Measurements for \ce{^{64}Cu} and \ce{^{47}Sc} at 2.76 MeV using a D-D Neutron Generator for Medical Isotope Studies

### 2016-12-30 First_np_Paper/first_np_paper.tex
Updated section 2.4 with first round edits

After irradiation, the co-loaded targets in each experiment were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy. Two detectors were used in this measurement: an Ortec 80\% High-Purity Germanium (HPGe) detector (calibrated from 50 keV - 3800 keV) used for the detection of the higher-energy gamma rays in the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} experiments, and an Ortec planar LEPS detector (calibrated from 15 keV - 450 keV) used for the detection of the lower-energy gamma rays in the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} experiments. These can be seen in \autoref{fig:hpge_a} and \autoref{fig:hpge_b}. Both detectors were calibrated for both energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector. These efficiencies, along with gamma ray intensities for each transition, are used to convert the counts in each detected gamma ray photopeak into an activity for the activated isotopes and isomeric states.

@@

For all data collection, performed using the Ortec MAESTRO software, the foils were counted in their polyethylene holder, and placed against the front face of the detector in use, with the target foil (zinc or titanium) facing towards the front face of the detector. This position allows for the detectors to subtend the largest possible solid angle of the gamma rays emitted by the foils. Before data was collected, detector dead time was verified to be less than 5\%, to avoid coincidence summing effects. This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector, to reduce the dead time.  For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector, and for the case of \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities. After approximately 4 hours of spectra collection, the activated zinc foil was added back and counting resumed simultaneously with the indium foil. This is due to the fact that the \ce{^{115}In} can undergo the \ce{^{115}In}(n,$\gamma$)\ce{^{116}In} reaction, with a cross section of 83 mb for 2.76 MeV neutrons. \ce{^{116}In} has a 54 minute half life, decaying via $\beta^-$ with a Q value of 3.278 MeV. This decay populates several states in \ce{^{116}Sn} capable of emitting gamma rays with $E_\gamma > 2 \times 511$  keV, which pair produce in the detector crystal, contaminating the 511-keV channel used to monitor  \ce{^{64}Cu} production. By waiting for 4 hours of counting the indium foil separately, nearly all \ce{^{116}In} will have decayed, making it safe to add the activated zinc foil without worries of significant 511 keV contamination. Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.

@@

To verify that each peak truly corresponds to assigned transitions, spectra collection for each foil was counted in a series of 15 - 30 minute sequential data acquisitions. By plotting the background-subtracted photopeak counts for a particular channel as a function of time, an exponentially decaying curve may be fit to it, to determine the half life of the transition in question. Plots of these curves for each transition in this work are seen in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511}. The fitted half lives in each of these curves has strong statistical agreement with accepted half lives from the ENDF-VII/B library, indicating that these peaks are the correctly assigned transitions.

@@

Background-subtracted counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.

>>>>

After irradiation, the co-loaded targets in each experiment were removed from the HFNG and transferred to a counting lab, where their induced activities could be measured via gamma ray spectroscopy. Two detectors were used in this measurement: an Ortec 80\% High-Purity Germanium (HPGe) detector (calibrated from 50 keV - 3800 keV) used for the detection of the higher-energy gamma rays in the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} experiments, and an Ortec planar Low-Energy Photon Spectrometer (LEPS) detector (calibrated from 15 keV - 450 keV) used for the detection of the lower-energy gamma rays in the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} experiments. These can be seen in \autoref{fig:hpge_a} and \autoref{fig:hpge_b}. Both detectors were calibrated for both energy and efficiency, using \ce{^{133}Ba}, \ce{^{137}Cs}, and \ce{^{152}Eu} sources at various distances from the front face of each detector. These efficiencies, along with gamma ray intensities for each transition, are used to convert the integrated counts in each gamma ray photopeak into an activity for the activated isotopes and isomeric states.

@@

The foils were counted in their polyethylene holder, and placed close to the front face of the detector in use, with the target foil (zinc or titanium) facing towards the front face of the detector when both target and monitor foils were counted simultaneously. This position allows for the detectors to subtend the largest possible solid angle of the gamma rays emitted by the foils. All data collection was performed using the Ortec MAESTRO software. For each experiment the detector dead time was verified to be less than 5\%, to avoid coincidence summing effects. This was never an issue for any experiments, but had it been, the foils would be moved to a position of greater standoff from the detector, to reduce the dead time.  For the  \ce{^{47}Sc} production experiments, the foils were counted simultaneously using a planar LEPS detector. For the \ce{^{64}Cu} production experiments, the Indium foil was first counted separately using an 80\% HPGe detector, to capture the short-lived Indium activities. This is due to the fact that the \ce{^{115}In} can undergo the \ce{^{115}In}(n,$\gamma$)\ce{^{116}In} reaction, with a cross section of 83 mb for 2.76 MeV neutrons. \ce{^{116}In} has a 54 minute half-life, decaying via $\beta^-$ with a Q value of 3.278 MeV. This decay populates several states in \ce{^{116}Sn} capable of emitting gamma rays with $E_\gamma > 2 \times$ the 511-keV gamma, which is produced via pair production in the detector crystal, contaminating the 511-keV channel used to monitor  \ce{^{64}Cu} production. After approximately 4 hours of spectra collection, the activated zinc foil was added back and counting resumed simultaneously with the indium foil. This allowed for decay of nearly all \ce{^{116}In}, avoiding significant 511 keV contamination. Example spectra for each production pathway can be seen in \autoref{fig:spectra_a} and \autoref{fig:spectra_b}.

@@

\comment{Example spectra are messy - being updated...}

To verify that each peak corresponds to the assigned transitions, spectra were acquired in a sequence of 15 - 30 minute intervals. By plotting the background-subtracted photopeak counts for a particular channel as a function of time, an exponential decay function may be fit to it, to determine the half-life of the transition in question. Plots of these curves for each transition in this work are seen in Figures \ref{fig:decay_curve_336} - \ref{fig:decay_curve_511}. The fitted functions for each transition agree (at the 1$\sigma$ confidence level) with accepted half-lives from the ENSDF library, confirming the respective peak assignments.

\comment{Reference original ENSDF papers?}

@@

The background-subtracted integrated counts in each photopeak, as well as the counting duration for each experiment, are tabulated in \autoref{tab:peak_counts}.
